Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra

### 2015-05-26 ms.tex
Minor change to HERA info in Sections 5 and 6
From 38cd004:
============

In ms.tex,

(*) Minor change to HERA info in Sections 5 and 6

The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly. With the SKA at low frequencies, plans to deploy ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas are being considered. The ``station beam'' will be obtained by a phased addition of the dipole responses. The typical horizon response of these beams is $\gtrsim$~30~dB lower than at zenith\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} but the randomness across different stations in the placement of dipoles is expected to reduce the response significantly further as pairs of station voltage beams are multiplied with each other. HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA. Their precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to their aperture designs which are in their final stages.

@@

For future work, we plan to extend our analysis to HERA. It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.

>>>>

The response of new instruments such as SKA and HERA to foreground contamination has to be investigated thoroughly. With the SKA at low frequencies, plans to deploy ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of 256 pseudo-randomly placed vertical log-periodic dipole antennas are being considered. The ``station beam'' will be obtained by a phased addition of the dipole responses. The typical horizon response of these beams is $\gtrsim$~30~dB lower than at zenith\footnote{SKA memo ``Station Response and Imaging Performance of LFAA: 100 MHz to 600 MHz'' by Razavi-Ghods et al.} but the randomness across different stations in the placement of dipoles is expected to reduce the response significantly further as pairs of station voltage beams are multiplied with each other. HERA will be a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. It will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA. Their precise beam responses and the resulting foreground contamination, especially near the horizon, will prove to be critical and timely inputs to their aperture designs which are in their final stages.

@@

For future work, we plan to extend our analysis to HERA. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
